\documentclass{article}

\begin{document}

\setlength{\parindent}{6ex}

\indent

You Only Look Once (YOLO) \cite{yolocite} refers to unified, real-time object detection. 
YOLO is called unified since it performs simultaneous prediction overall image using its 
fixed number of bounding boxes in each grid cell. Also, the whole detection pipeline is a 
single network, thus YOLO can be optimized end-to-end directly from a given image to its 
detection performance. \par

The process of prediction can be examined as follows:
\begin{enumerate}
    \item The given image is split into the SxS grid.
    \begin{itemize}
        \item Each grid cell is responsible for the prediction of one object.
The selection of which cell is responsible is chosen by the center of 
the object. If an object's center falls into a cell, that cell is 
responsible to predict that object.
    \end{itemize}
    \item Each grid cell has B bounding boxes to make a prediction.
    \begin{itemize}
        \item One prediction for each grid cell, independent of the number of 
bounding boxes, causes YOLO to predict a limited number of objects when 
there are multiple objects present in a grid cell.
    \end{itemize}
    \item Thus, YOLO predicts B bounding boxes and one confidence score for 
each grid cell. Now, let's get into more detail for these predictions:
    \begin{itemize}
        \item For each of these bounding boxes, five values are predicted:
x, y, w, h, and confidence score. The values x and y are the corresponding object's 
center coordinates on the given image. The values w and h are corresponding object's 
width and height. The confidence score refers to detector's confidence whether an 
object exists in the corresponding bounding box and how accurate the bounding box is.
        \item The values x and y are normalized relative to the cell they belong and 
the values w and h are normalized relative to the given image, so that, all these 
x, y, w, and h values are between 0 and 1. Also, a class conditional probability for 
each grid cell is predicted. Thus, each category in the possible class set has one 
class conditional probability in each grid cell. 
        \item Thus, for SxS grid and B bounding boxes for each grid cell, 
predictions are encoded as S x S x (B * 5 + C) tensor.
    \end{itemize}
\end{enumerate}
\end{document}